% !TeX spellcheck = en_UK
\documentclass[11pt,a4paper,twoside]{article}

%tilføj bibliografi
\usepackage{csquotes}
\usepackage[backend=biber, sortlocale=en_UK, sortcites]{biblatex}
\addbibresource{mini.bib}

\usepackage[danish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{makeidx}
\usepackage{multind} %lav flere indexer
\usepackage{amssymb, amsmath, amsfonts}
\usepackage[section]{placeins} %tabeller og figurer flyder kun indenfor egen sektion
\usepackage{graphicx} % .png, .jpg etc kan embeddes i dokumentet
\usepackage[a4paper, bmargin=2cm]{geometry}
\usepackage{float} %Placer floats præcist med specifier'en "H"
\usepackage{caption} %kontroller "caption" bedre
\usepackage{subcaption} %lav captions i subfloats
\usepackage{paralist} %gør lister mere fleksible
\usepackage{wasysym} %lav smileys

\usepackage{endnotes} %lav slutnoter
\renewcommand{\notesname}{Noter} %omdøb overskriften for slutnote-afsnittet

\usepackage{multirow} %slå flere rækker i en tabel sammen til én
\usepackage{collect} %Indhent tekst til senere brug
\usepackage{placeins} %hold floats indenfor barrierer
\usepackage{import} %erstatter \include{} og \input{} af subfolders
\setcounter{secnumdepth}{4} %nummerer helt ned til subsubsection
\setcounter{tocdepth}{4} %indholdsfortegnelse helt ned til subsubsection

\newcommand{\bs}{\textbackslash} % skriv "\" uden at få skrivekrampe

%\author{Klaus Wogelius}
\title{Letter of application for the\\ position as Telecom Field Engineer}
\begin{document}
\maketitle
\subsection*{Dear Mrs. Selsøe}
I am writing to you to express my interest in the Telecom Field Engineer position currently available at Blue Town.
\par
I believe that I am fit for this position due to many years of experience in planning, installing, commissioning and handover of Telecom equipment from the Installation Department to the Maintenance Department of Tele Greenland.
\par
In your job description most items stood out to me as very alike the daily tasks of my current job as Project Engineer. Tasks like:
\begin{compactitem}
\item technical deployment and supervision of suppliers (civil works on-site),
\item commissioning of deployed installations,
\item supplier follow up and management,
\item quality assurance of the technical installations,
\item antenna adjustment, and
\item involvement in completing documentation, developing test, commissioning documentation and ensuring the necessary documentation in order to carry out the installation, are familiar to me.
\end{compactitem}
\par
I also comply to your requirement for:
\begin{compactitem}
\item relevant technical educational background. 
\item minimum 3 years experience with similar tasks - preferably from a Telecom company installing for example 3G or 4G network\footnote{As mostly involved in backbone and access radio - and IP Core network I am yet to have installed any 3G or 4G network.}.
\item leadership experience and experience from working with different cultures.
\end{compactitem}
\par
I am experienced, dedicated and self-driven - believing to have the overview and flair for technique and mechanical design. I am used to travelling activity as part of my job.
\par
After you have reviewed my application and resume I believe that you will see that I possess a skill set which matches your requirements almost perfectly. If you have any further questions or require additional documentation, please feel free to contact me.\\[.2cm]
Thank you for your time and consideration.\\[.2cm]
Respectfully
\\[.2cm]
Klaus Wogelius\\
\textit{E-mail:} kw@tele.gl\\
\textit{Cell phone:} +299 54 27 85\\


\printbibliography[title=Referencer]
\end{document}